Actuator line modeling of vertical-axis turbines

### 2016-05-05 paper.tex
PhD --> doctoral
Fix typo forces --> force

Assuming unsteady effects can be appropriately modeled, the blade element lift force, drag forces, and pitching moment are calculated as
\begin{equation}
    F_l = \frac{1}{2} \rho A_\mathrm{elem} C_l |\vec{U}_\mathrm{rel}|^2,
\end{equation}
\begin{equation}
    F_d = \frac{1}{2} \rho A_\mathrm{elem} C_d |\vec{U}_\mathrm{rel}|^2,
\end{equation}
\begin{equation}
    M = \frac{1}{2} \rho A_\mathrm{elem} c C_m |\vec{U}_\mathrm{rel}|^2,
\end{equation}
respectively, where $\rho$ is the fluid density, $A_\mathrm{elem}$ is the blade
element planform area (span $\times$ chord), $\vec{U}_\mathrm{rel}$ is the local
relative velocity projected onto the plane of the element profile cross-section
(i.e., the spanwise component is neglected), and $C_l$, $C_d$, and $C_m$ are the
sectional lift, drag, and pitching moment coefficients, respectively, which are
linearly interpolated from a table per the local angle of attack. The forces are
then projected onto the rotor coordinate system to calculate torque, overall
drag, etc. Forces from the turbine shaft and blade support struts are computed
in a similar way. After the force on the actuator lines from the flow is
computed, it is then added to the Navier--Stokes equations as a body force or
momentum source (per unit density, assuming incompressible flow):
\begin{equation}
    \frac{\mathrm{D} \vec{u}}{\mathrm{D} t} = - \frac{1}{\rho} \nabla p + \nu
    \nabla^2 \vec{u} + F_\mathrm{turbine}.
\end{equation}

@@

\acks The authors would like to acknowledge funding through a National Science
Foundation CAREER award (principal investigator Martin Wosnik, NSF 1150797,
Energy for Sustainability, program manager Gregory L. Rorrer). This work has
been carried out as part of author P. Bachant's PhD research at the University
of New Hampshire.

>>>>

Assuming unsteady effects can be appropriately modeled, the blade element lift
force, drag force, and pitching moment are calculated as
\begin{equation}
    F_l = \frac{1}{2} \rho A_\mathrm{elem} C_l |\vec{U}_\mathrm{rel}|^2,
\end{equation}
\begin{equation}
    F_d = \frac{1}{2} \rho A_\mathrm{elem} C_d |\vec{U}_\mathrm{rel}|^2,
\end{equation}
\begin{equation}
    M = \frac{1}{2} \rho A_\mathrm{elem} c C_m |\vec{U}_\mathrm{rel}|^2,
\end{equation}
respectively, where $\rho$ is the fluid density, $A_\mathrm{elem}$ is the blade
element planform area (span $\times$ chord), $\vec{U}_\mathrm{rel}$ is the local
relative velocity projected onto the plane of the element profile cross-section
(i.e., the spanwise component is neglected), and $C_l$, $C_d$, and $C_m$ are the
sectional lift, drag, and pitching moment coefficients, respectively, which are
linearly interpolated from a table per the local angle of attack. The forces are
then projected onto the rotor coordinate system to calculate torque, overall
drag, etc. Forces from the turbine shaft and blade support struts are computed
in a similar way. After the force on the actuator lines from the flow is
computed, it is then added to the Navier--Stokes equations as a body force or
momentum source (per unit density, assuming incompressible flow):
\begin{equation}
    \frac{\mathrm{D} \vec{u}}{\mathrm{D} t} = - \frac{1}{\rho} \nabla p + \nu
    \nabla^2 \vec{u} + F_\mathrm{turbine}.
\end{equation}

@@

\acks The authors would like to acknowledge funding through a National Science
Foundation CAREER award (principal investigator Martin Wosnik, NSF 1150797,
Energy for Sustainability, program manager Gregory L. Rorrer). This work has
been carried out as part of author P. Bachant's doctoral research at the
University of New Hampshire.
